Replicate earlier study

### 2023-04-02 x_replicate.qmd
added tesselation of study data with H3

source("~/RProjects/paper-2023-ICNS/R/assign_threshold_time2.R")
source("~/RProjects/paper-2023-ICNS/R/identify_threshold_overhead.R")
source("~/RProjects/paper-2023-ICNS/R/add_bearing_to_target.R")
source("~/RProjects/paper-2023-ICNS/R/estimate_threshold_time.R")
source("~/RProjects/paper-2023-ICNS/R/identify_threshold_overhead.R")
source("~/RProjects/paper-2023-ICNS/R/add_landing_time_to_nested_data.R")
```

@@

  with_ldg_time <-  arrs |>
    dplyr::mutate(
      study_trj = pmap(
              .l = list(data, UID, RWY)
            , .f = ~ add_landing_time_to_nested_data(..1, ..2, ..3, rwys)
            )
      ) |> 
   # dplyr::mutate(study_trj = map(.x = study_trj, .f = ~ interpolate_lin_4D(.x, .source = "OSN"))) |> 
    dplyr::mutate(ALDT = map(.x = study_trj, .f = ~ filter(.x, MST == "ALDT") |> pull(TIME))) |> tidyr::unnest(ALDT)

@@

>>>>

source("~/RProjects/paper-2023-ICNS/R/assign_threshold_time2.R")
source("~/RProjects/paper-2023-ICNS/R/identify_threshold_overhead.R")
source("~/RProjects/paper-2023-ICNS/R/add_bearing_to_target.R")
source("~/RProjects/paper-2023-ICNS/R/estimate_threshold_time.R")
source("~/RProjects/paper-2023-ICNS/R/identify_threshold_overhead.R")
source("~/RProjects/paper-2023-ICNS/R/add_landing_time_to_nested_data.R")

# set ggplot theme
ggplot2::theme_set(ggplot2::theme_minimal())
```

@@

  with_ldg_time <-  arrs |>
    # estimate and assign landing time to arrival trajectories
    dplyr::mutate(
      study_trj = pmap(
              .l = list(data, UID, RWY)
            , .f = ~ add_landing_time_to_nested_data(..1, ..2, ..3, rwys)
            )
      ) |> 
    # pullout ALDT as separate column
    dplyr::mutate(
      ALDT = map(.x = study_trj
               , .f = ~ filter(.x, MST == "ALDT") |> pull(TIME)
               )
      ) |> tidyr::unnest(ALDT) |> 
    # interpolate to 5sec
    dplyr::mutate(
      study_trj = map(.x = study_trj
                    , .f = ~ interpolate_lin_4D(.x, .source = "OSN") |> 
                             add_time_and_distance_to_go() |> 
                             dplyr::mutate(H3_BIN = h3::geo_to_h3(c(LAT, LON), res = 8))
                    )
      )

@@

```{r}
study_sequences |> filter(LEAD_DELTA < 500) |> 
  ggplot() +
  geom_boxplot(aes(x = RWY, y = LEAD_DELTA))
```

```{r}
study_sequences <- mickey |> filter(ARR, !ORPHAN) |> select(UID, RWY, ALDT) |> 
  arrange(RWY, ALDT, UID) |> 
  group_by(RWY) |> 
  mutate(
     LEAD_DELTA = difftime(ALDT, lag(ALDT, default = first(ALDT)), units = "sec")
    ,INTERACT   = LEAD_DELTA < 240
    ,LEADER     = ifelse(INTERACT, lag(UID), NA)) |> 
  ungroup()
study_sequences
```

write-out tesselation data for reference times

```{r}
tessel_fn <- here::here("data", "EGLL-tessel-db.csv.gz")

extract_tessel_info <- function(.study_trj, ...){
  df <- .study_trj
  df <- df |> dplyr::select(H3_BIN, TIME_2GO, DIST_2GO )
}

make_tessel_db_entry <- function(.study_trj, .ptn = ptn, ...){
  df <- .study_trj |> 
    dplyr::select(UID, RWY, study_trj) |> 
    dplyr::mutate(UID = paste(UID, gsub("-", "", .ptn), sep = "-")) |> 
    dplyr::mutate(
      info = purrr::map(
                .x = study_trj
              , .f = ~ extract_tessel_info(.x)
              )
      ) |> 
    tidyr::unnest(info)
  return(df)
}
```

```{r}
tessel_info <- make_tessel_db_entry(mickey |> filter(ARR, !ORPHAN))
tessel_info
```

```{r}
ti <- tessel_info |> ungroup() |> 
  select(-study_trj) |> 
  group_by(H3_BIN) |> summarise(N = n(), .groups = "drop") |> 
  mutate(
    # add geometry column without naming column (easier than fixing it afterwards)
    h3::h3_to_geo_boundary_sf(H3_BIN)
    ) |> 
  sf::st_as_sf()

p1 <- ggplot() +
  geom_sf(data = ti, aes(fill = N), color = NA) + 
  scale_fill_distiller(palette = "Spectral")

leftright <- 0.3
p2 <- p1 +
  coord_sf( xlim = c(arp_egll$LON - leftright, arp_egll$LON + leftright)
           ,ylim = c(arp_egll$LAT - leftright, arp_egll$LAT + leftright)
           )

library(patchwork)
p1 + p2 +
  plot_layout(guides = 'collect') &
  theme(legend.position = "top")
```
